\documentclass[colibri]{mcdowellcv}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  filecolor=magenta,
  urlcolor=cyan,
}

\name{Francisco Soto}
\address{Sonora, Mexico\linebreak(MST)}
\contacts{
  ebobby@ebobby.org
  \linebreak
  \href{https://ebobby.org}{https://ebobby.org}
  \linebreak \href{https://github.com/ebobby}{https://github.com/ebobby}
}

\begin{document}
\makeheader
\begin{cvsection}{About}
  \begin{cvsubsection}{}{}{}
    Seeking an engineering lead role. Experienced in building a wide variety of
    software products in fast-paced environments on domains like B2B SaaS, EdTech,
    FinTech, and HealthTech. Deep technical knowledge ranging from architecture to
    implementation and demonstrated ability to lead and guide teams.

    Deeply curious and life long learner. I take pleasure in figuring things out
    and deeply understanding them. I have a bias for action and
    \textbf{\textit{getting things done}}.
	\end{cvsubsection}
\end{cvsection}
\begin{cvsection}{Experience}
	\begin{cvsubsection}{Staff Software Engineer}{Aspire (remote)}{Jan 2022 -- March 2023}
    Aspire is a robust marketing platform that helps ecommerce brands build
    influential creator communities and manage marketing campaigns. As a Staff
    Engineer, I joined a ~35 engineer team with a mission to execute the company's
    technical vision, mentor engineers, and lead cross-team projects.
    \newline
		\begin{itemize}
    \item
      I developed and integrated the first version of our creator platform with
      Instagram Creator Marketplace. This enabled our users to use Instagram
      Direct Messaging for campaign communications, streamlining the
      process. The project was developed in collaboration with Meta, providing
      Aspire with strategic access to exclusive features and data on Instagram
      creators.
    \item
      I led the implementation of back-end services testing, setting up CI/CD
      support core libraries, scaffolding, and configuration. I performed demos,
      provided code examples, and one-on-one mentoring. The initiative resulted
      in a decrease in bug reports and severity of issues, minimized product
      downtime, and increased development velocity.
		\end{itemize}
  \end{cvsubsection}
	\begin{cvsubsection}{Senior Software Engineer}{dumpling (remote)}{Nov 2020 -- Dec 2021}
    Dumpling is a platform that provides tools to help individuals start, run, and
    grow their local shopping and delivery businesses. As an early stage team
    member I took charge of improving the shopping product database.
    \newline
		\begin{itemize}
    \item
      Developed internal tools for managing the store and product catalog, as
      well as related features. These tools were instrumental in reducing the
      turnaround time needed to resolve data quality issues, resulting in a more
      efficient and streamlined process.
    \item
      Designed and implemented a search-based recommendations engine. By
      delivering relevant results to new buyers, we were able to improve
      engagement metrics and significantly reduce the churn rate.
		\end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Senior Software Engineer}{Homeroom (remote)}{Mar 2019 -- Sep 2020}
    Homeroom is an all-in-one platform to set-up, manage and shop for enrichment
    activities after school. Joined as an engineer and tech lead to scale the
    current platform and build new features.
    \newline
		\begin{itemize}
    \item
      By redesigning the locking strategy and fine-tuning the production
      environment, I was able to optimize backend performance by 300\% during
      peak load. This resulted in increased sales and a 50\% reduction in
      infrastructure costs.
    \item I developed a command-line tool that enabled the creation and
      deployment of isolated testing environments. By testing each feature
      individually rather than all at once, this streamlined our process,
      minimized conflicts, and increased our development velocity.
    \item As a mentor, I provided guidance to team members, conducted thorough
      code reviews, and offered support with architecture and system
      design. Fostered a culture of collaboration and continuous improvement
      within the team.
		\end{itemize}
	\end{cvsubsection}
  \newpage
	\begin{cvsubsection}{Senior Software Engineer}{CareZone (remote)}{Jul 2015 -- Dec 2018}
    CareZone was a consumer healthcare startup that simplified medication and health
    information management, offering additional services like pharmacy and insurance
    support.
    \newline
		\begin{itemize}
    \item
      Designed and implemented a comprehensive data synchronization scheme that is
      utilized across all Carezone systems. This includes the API that serves our
      mobile applications, pharmacy, insurance, and e-commerce platforms.
    \item
      Improved application performance by identifying and addressing performance
      bottlenecks, optimizing database queries and indexing. This improved
      application response times by 25\%.
    \item
      As a technical lead, I provided guidance for team members, organized
      internal tech talks, and led small teams.
		\end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Founder}{Chopeo (Mexico)}{Apr 2014 -- May 2015}
    I co-founded Chopeo, a DIY ecommerce platform for Latin America, offering
    order management, payments, and shipping integration.\
    \newline
		\begin{itemize}
    \item
      Co-founded company, made key hires, managed the technical team, secured
      angel investment, and established strategic partnerships.
    \item
      I developed the backend for our main product, a multi-tenant e-commerce service
      that supported over 250 micro-businesses, generating over \$2.5M MXN in
      sales during the first year.
		\end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Spacecraft Software Engineer}{Spire Global (San Francisco, CA)}{Aug 2013 -- Nov 2013}
    Spire Global operates the largest multipurpose constellation of satellites,
    offering advanced space-to-cloud analytics for maritime, aviation, and weather
    tracking.
    \newline
    \begin{itemize}
    \item
      I developed Ardusat2's ground-to-satellite radio module firmware within four
      months, contributing to a record-breaking design-to-implementation timeline for
      the satellite project.
		\end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Senior Software Engineer}{Expensify (San Francisco, CA)}{Feb 2013 -- Jun 2013}
		\begin{itemize}
    \item
      Implemented new features and bank integrations, expanding the customer base.
    \item
      Led SQL training for marketing and sales, resulting in improved targeted
      ad campaigns.
    \item
      Optimized database queries to meet strict SLAs through careful application
      profiling.
		\end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Engineering Manager}{INgrooves (San Francisco, CA)}{Apr 2009 -- Dec 2012}
    Ingrooves empowers music labels and entrepreneurs to grow their businesses
    through distribution, marketing, analytics, rights management, royalty
    accounting, and licensing solutions.
    \newline
		\begin{itemize}
    \item
      Led technical teams on major company-wide projects.
    \item
      Bootstrapped INscribe Digital, an ebook distribution platform, generating
      new revenue.
    \item
      Designed enterprise-level system for album ingestion, facilitating
      distribution of valuable musical properties.
    \end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Senior Software Engineer}{Nearsoft (Mexico)}{Aug 2008 -- Sep 2009}
		\begin{itemize}
    \item
      Created an online real-time chat platform for a price haggling startup.
		\end{itemize}
	\end{cvsubsection}
	\begin{cvsubsection}{Senior Software Engineer}{CIDIA (Mexico)}{Feb 2006 -- Aug 2008}
		\begin{itemize}
    \item
      Created an image processing, analysis, and 3D rendering app to aid optical
      profilometry research.
    \item
      Led a team that developed a meat grade classifier using advancing computer
      vision to improve a Mexican slaughterhouse grading process.
    \item
      Designed and built a coffee bean roasting level prototype device.
		\end{itemize}
	\end{cvsubsection}
  \begin{cvsubsection}{Keywords}{}{}
    Backend, Linux, Cloud, SQL, Redis, Rust, Lisp, Python, Ruby, Go, C
  \end{cvsubsection}
\end{cvsection}
\end{document}

%%% Local Variables:
%%% TeX-engine: luatex
%%% TeX-master: t
%%% End:
